---
title: "Using eemont and geemap in R with rgee"
output: html_notebook
---

# Using eemont and geemap in R with rgee

- GitHub Repo: [https://github.com/davemlz/eemont](https://github.com/davemlz/eemont)
- PyPI link: [https://pypi.org/project/eemont/](https://pypi.org/project/eemont/)
- Documentation: [https://eemont.readthedocs.io/en/0.1.7/index.html](https://eemont.readthedocs.io/en/0.1.7/index.html)

## Let's start!

Import the required packages:

```{r}
library(rgee)
library(reticulate)
```

Initialize GEE:

```{r}
ee_Initialize()
```

If required, please uncomment:

```{r}
#py_install("eemont")
#py_install("geemap")
```

Import *eemont* and *geemap.colormaps*:

```{r}
eemont <- import("eemont")
cm <- import("geemap.colormaps")
```

Point of interest:

```{r}
point <- ee$Geometry$Point(c(-74.0592,11.3172))
```

Get and filter the Landsat 8 SR collection:

```{r}
L8 <- ee$ImageCollection('LANDSAT/LC08/C01/T1_SR')$filterBounds(point)
```

## Using *eemont*:

The same Python methods can be used here. Remember to change "." for "$":

```{r}
L8 <- L8$maskClouds()$scale()$index("NDWI")
```

## Visualization (let's use the colormaps from *geemap*)

Let's define the visualization:

```{r}
visParamsNDWI <- list(
  min = 0,
  max = 1,
  bands = "NDWI",
  palette = cm$get_palette("Spectral_r") # Matplotlib colormap from geemap
)
```

Display results:

```{r}
Map$centerObject(point,8)
Map$addLayer(L8$first(),visParamsNDWI,"L8 NDWI")
```
